A geographic routing approach for IPv6 in low-powered and lossy large-scale wireless networks

### 2015-04-06 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
figuras colocadas no mesmo diretorio do arquivo .tex (necessário para upload do .tex no sistema da revista)
definição do estilo de bibliografia (necessário para upload no sistema da revista)
atualização da biografia

\begin{figure}[h!tb]
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/RPL_DIO}
\else
\includegraphics[width=0.8\textwidth]{figures/RPL_DIO}
\fi
\caption{Example of a Destination Oriented Directed Acyclic Graph(DODAG).}
\label{RPL_DIO}
\end{figure}

@@

\begin{figure}[h!tb]
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/RPL_DAO}
\else
\includegraphics[width=1\textwidth]{figures/RPL_DAO}
\fi
\caption{P2P communication between routers $B$ and $C$ through a DODAG root using RPL.}
\label{RPL_DAO}
\end{figure}

@@

\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/sample_scenarios.eps}
\else
\includegraphics[width=1\textwidth]{figures/sample_scenarios.eps}
\fi
\caption{Sample of simulated scenarios with nodes populated.}
\label{sim_scenarios}
\end{figure}

\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/hops_range.eps}
\else
\includegraphics[width=1\textwidth]{figures/hops_range.eps}
\fi
\caption{Simulation results of the average route length for the routing algorithms (RPL, GOAFR, \textit{GeoRank}, and Dijkstra' algorithm for shortest path).}
\label{sim_results}
\end{figure}

@@

\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/mem_usage_range.eps}
\else
\includegraphics[width=1\textwidth]{figures/mem_usage_range.eps}
\fi
\caption{Simulation results of the size of the routing table in number of entries relative to the number of nodes in the network, for the routing algorithms RPL and \textit{GeoRank}}
\label{sim_results2}
\end{figure}

@@

\bibliographystyle{bst_models/model2-names}
\bibliography{refs}

@@

\noindent {\bf Gustavo Weber Denardin}
received his B.Eng., M.Eng. and Ph.D. degrees in Electrical Engineering from Federal University of Santa Maria, Brazil, in 2002, 2004 and 2012, respectively. He joined the Department of Electronics at Federal University of Technology - Parana (UTFPR) in 2005, where he is currently an associate professor. His research interests include embedded systems, Real-time Operating Systems, wireless sensor/actuator networks and its applications in lighting and power systems.\newline

>>>>

\begin{figure}[h!tb]
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/RPL_DIO}
\else
\includegraphics[width=0.8\textwidth]{RPL_DIO}
\fi
\caption{Example of a Destination Oriented Directed Acyclic Graph(DODAG).}
\label{RPL_DIO}
\end{figure}

@@

\begin{figure}[h!tb]
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/RPL_DAO}
\else
\includegraphics[width=1\textwidth]{RPL_DAO}
\fi
\caption{P2P communication between routers $B$ and $C$ through a DODAG root using RPL.}
\label{RPL_DAO}
\end{figure}

@@

\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/sample_scenarios.eps}
\else
\includegraphics[width=1\textwidth]{sample_scenarios.eps}
\fi
\caption{Sample of simulated scenarios with nodes populated.}
\label{sim_scenarios}
\end{figure}

\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/hops_range.eps}
\else
\includegraphics[width=1\textwidth]{hops_range.eps}
\fi
\caption{Simulation results of the average route length for the routing algorithms (RPL, GOAFR, \textit{GeoRank}, and Dijkstra' algorithm for shortest path).}
\label{sim_results}
\end{figure}

@@

\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/mem_usage_range.eps}
\else
\includegraphics[width=1\textwidth]{mem_usage_range.eps}
\fi
\caption{Simulation results of the size of the routing table in number of entries relative to the number of nodes in the network, for the routing algorithms RPL and \textit{GeoRank}}
\label{sim_results2}
\end{figure}

@@

\bibliographystyle{model2-names}
\bibliography{refs}

@@

\noindent {\bf Gustavo Weber Denardin}
received his B.Eng., M.Eng. and Ph.D. degrees in Electrical Engineering from Federal University of Santa Maria, Brazil, in 2002, 2004 and 2012, respectively. He joined the Department of Electronics at Federal University of Technology - Parana (UTFPR) in 2005, where he is currently an associate professor. His research interests include embedded systems, Real-time Operating Systems and wireless sensor/actuator networks.\newline
